### 2022-11-13 NSF2022/Description/broaderimpacts.tex
suggested reviewers

\section{Broader Impacts}
\label{sec:BroaderImpacts}
This project aims to advance the mathematical modeling of collective dynamics of amphiphilic particles. The simulations use a new, yet intuitive, approach that accounts for important and complex systems that are presently out of reach in computational material science. These complex systems include optimal shape design in metamaterials and fusion and fission of amphiphilic bilayer membranes. The models describing colloidal systems could be transformative in biomedicine and material science. The research draws from expertise in scientific computing, physics of fluids, and mathematics. The mathematical component incorporates leading variational techniques and offers insight into fundamentals of material science. The project brings socially consequential research into the classroom and offers 
undergraduates the opportunity to train alongside faculty and graduate students. With its combination of mathematical modeling, analysis, and scientific computing, the project highlights the importance of mathematics and computation to all areas of science and engineering.

>>>>

\section{Broader Impacts}
\label{sec:BroaderImpacts}
This project aims to advance the mathematical modeling of collective
dynamics of amphiphilic granules. The framework uses a new PDE-based
formulation and fast and accurate computational techniques that account
for important and complex systems in
soft matter.  These complex systems include
optimal shape design in metamaterials and fusion and fission of amphiphilic
bilayer membranes. The models describing colloidal systems could be
transformative in biomedicine and material science.
The research draws from
expertise in scientific computing, physics of fluids, and mathematics. The
mathematical component incorporates leading variational techniques and offers
insight into fundamentals of material science. The project brings socially
consequential research into the classroom and offers 
undergraduates the opportunity to train alongside faculty and graduate students.
With its combination of mathematical modeling, analysis, and scientific computing,
the project highlights the importance of mathematics and computation to all areas
of science and engineering.
